Title

### 2023-09-09 main.tex
Comentarios editor

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\FXRegisterAuthor{tb}{ttb}{\color{green}TB}

@@

@@

Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
and withing them, the simplest class of channels that produce decoherence are
Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
effective models for the noise affecting quantum devices~\cite{Flammia}.

To represent the algorithms implemented in quantum computers, either to
simulate a physical system or for some other purpose, one often uses a quantum
circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
quantum circuits, that is,  quantum circuits in which some of the operations
depend on variable parameters~\cite{cerezo}.  These circuits play an important
part in applications such as quantum machine learning~\cite{Benedetti} and
describing general quantum transformations dependent on parameters. Substantial
research has been devoted to enhancing the efficiency of these
circuits~\cite{Rasmussen}.

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the condition that only a
controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

We can also see how an arbitrary Pauli channel acts on an arbitrary  
density matrix.
To do it, we substitute \eref{eq: Density Matrix} 
in \eref{eq: Pauli channel 1 qbit}:
\begin{equation}
\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
\end{equation}
This can be simplified by using the following property of Pauli matrices:
\begin{equation}
\label{eq: propiedad-pauli}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 &-1 \\
1 & -1 & 1 & -1 \\
1 & -1 & -1 & 1
\end{pmatrix},
\end{equation}
which leads to
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
This gives us another way of understanding Pauli channels
as operations that take each component $r_{\alpha}$
of the density matrix and multiplies them
by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
that is:
\begin{equation}
\label{eq: multipliers}
r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
\end{equation}
Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
and ensures that after the channel, the resulting density matrix still has trace one. 
Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
Then, using that $k_{\gamma} \geq 0$
we get the following conditions on the multipliers $\tau_{\alpha}$:
\begin{eqnarray}
\label{eq: conditions-tetrahedron}
&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
\end{eqnarray}

@@

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
We find that close to the depolarizing channel, the general circuit simulator 
can implement such channels with the highest fidelity. 
% produce the highest 
% }}} 
\subsection{Description of the circuit for a Pauli channel} %{{{
\label{subsec: Description of the circuit}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_general.pdf}
\caption{{\bf Circuit for an $N$-qubit
Pauli channel.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
\label{Fig1}
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{Fig1}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the Ancilla State of
of \eref{eq: state} for the two ancilla qubits.
}
\label{Fig2} 
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/fig-tetra.pdf}
\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
to the center of the tetrahedron have high fidelities, while those close to the
borders do not.  Moreover, we show the results for cuts of the tetrahedron at
different values of $\tau_3$.}
\label{Fig3}
\end{figure} % }}}

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$.  This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{Fig2} is not optimal for
unitary channels (that is, the channels corresponding to the vertices of the
tetrahedron).  These straightforward channels could be accomplished more
efficiently by simply applying the corresponding Pauli operation directly.
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios.

@@

\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
circuit that includes only one gate dependent on a parameter $p$.
Moreover, the parametrized gate is a one-qubit rotation about any axis,
whether controlled or not.
\end{definition}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/OPR-circuit.pdf}
\caption{\textbf{General form of a 1PR circuit}.
Any 1PR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter.}
\label{Fig4}
\end{figure} % }}}

@@

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any 1PR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the
target qubit for the rotation, since if it weren't, we could use
swap gates to move the rotation
to the first qubit without adding gates
that depend on $p$.

@@

\begin{theorem}
\label{theorem2}
Consider a 1PR circuit of $N$ qubits parametrized by $p$
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
\end{align*}
with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
c^j|c^j \rangle = 1$.
\end{theorem}
\textbf{Proof:} 
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
with $B_{i,j}$ the entries of matrix $B$.
This can be rewritten by separating last qubit from the other $N-1$:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{align}
B|j\rangle = 
   \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle 
                                     + B_{2k+1,j} |k \rangle |1\rangle  \right) 
   + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  
                                      + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align}

Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle,
\end{align}
where we defined
\begin{align*}
|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align*}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

@@

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{Fig4}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. The operators $A$ and $B$ can be defined as follows:
\begin{align*}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\end{align*}
The remaining part of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary.
By starting from the initial state $|0\rangle$ and 
applying the circuit shown in \fref{Fig4}, straightforward calculations 
lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.

To see it, we can rewrite the expression of $B|0\rangle$ by 
separating the first $N-1$ qubits from the last one:
$$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
Since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain:

>>>>

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\FXRegisterAuthor{tb}{ttb}{\color{green}TB}
\FXRegisterAuthor{ed}{eed}{\color{red}ED}

@@

% Citar a estos manes de alguna manera y pedir que nos citen;
% https://mail.google.com/mail/u/0/#inbox/FMfcgzGtwgbtTGtlXkBtrCGQRxjRZrph

@@

Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
and within them, the simplest class of channels that produce decoherence are
Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
effective models for the noise affecting quantum devices~\cite{Flammia}.

To represent the algorithms implemented in quantum computers, either to
simulate a physical system or for some other purpose, one often uses a quantum
circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
quantum circuits, that is,  quantum circuits in which some of the operations
depend on variable parameters~\cite{cerezo}.  These circuits play an important
part in applications such as quantum machine learning~\cite{Benedetti} and
describing general quantum transformations dependent on parameters. Substantial
research has been devoted to enhancing the efficiency of these
circuits~\cite{Rasmussen}.  \\

\ednote{I fail to see the point here - the logic of the paper is: 
1."open quantum systems can be modeled through a class of channels representing he various types of decoherence. 2. Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.
3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them. \\
What I am missing is what do we learn by doing it which can't be learned by actually performing the Pauli channel onto a quantum system? For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial. Why would I need to decompose (not even effectively for any channel) the Pauli channels to match a gate based description? Which class of problems can we simulate that cannot be simulated otherwise? Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)\\
Intuitively, it seems incredibly harder resource wise to create the sum $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the restriction that only a
controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

We can also see how an arbitrary Pauli channel acts on an arbitrary  
density matrix.
To do it, we substitute \eref{eq: Density Matrix} 
in \eref{eq: Pauli channel 1 qbit}:
\begin{equation}
\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
\end{equation}
This can be simplified by using the following property of Pauli matrices:
\ednote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}

\tbnote{Una posible forma de escribirlo  (que no es con lo de Levi Civita, pero es que con lo de Levi Civita creo que quedaría muy complicado)}
{\color{green}
\begin{equation*}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   (-1)^{(1-\delta_{0\gamma}) (1-\delta_{\alpha 0}) (1-\delta_{\alpha \gamma })} \sigma_{\alpha}
\end{equation*}
}

\begin{equation}
\label{eq: propiedad-pauli}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 &-1 \\
1 & -1 & 1 & -1 \\
1 & -1 & -1 & 1
\end{pmatrix},
\end{equation}
which leads to
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix} \ednote{eq 2} \tbnote{No, sí es la eq 1}
but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
This gives us another way of understanding Pauli channels
as operations that take each component $r_{\alpha}$
of the density matrix and multiplies them
by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
that is:
\begin{equation}
\label{eq: multipliers}
r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
\end{equation}
Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
and ensures that after the channel, the resulting density matrix still has trace one. 
Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
Then, using that $k_{\gamma} \geq 0$
we get the following conditions on the multipliers $\tau_{\alpha}$:
\begin{eqnarray}
\label{eq: conditions-tetrahedron}
&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
\end{eqnarray}

@@

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels. \ednote{At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.}  Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
We find that close to the depolarizing channel, the general circuit simulator 
can implement such channels with the highest fidelity. 
% produce the highest 
% }}} 
\subsection{Description of the circuit for a Pauli channel} %{{{
\label{subsec: Description of the circuit}

@@

\begin{figure} % {{{
\centering
\includegraphics{circuito_general.pdf}
\caption{{\bf Circuit for an $N$-qubit
Pauli channel.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
\label{Fig1}
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\includegraphics{circuito_unqubit.pdf}
\caption{
{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{Fig1}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the Ancilla State of
of \eref{eq: state} for the two ancilla qubits.
}
\label{Fig2} 
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\includegraphics{fig-tetra.pdf}
\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
to the center of the tetrahedron have high fidelities, while those close to the
borders do not.  Moreover, we show the results for cuts of the tetrahedron at
different values of $\tau_3$.}
\label{Fig3}
\end{figure} % }}}

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. \ednote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. }  This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{Fig2} is not optimal for
unitary channels \ednote{why?} (that is, the channels corresponding to the vertices of the
tetrahedron).  These straightforward channels could be accomplished more
efficiently by simply applying the corresponding Pauli operation directly. \ednote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \ednote{but this is a severe disadvantage, that begs the question: what is the advantage?}

@@

\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
circuit that includes only one gate dependent on a parameter $p$.
Moreover, the parametrized gate is a one-qubit rotation about any axis,
whether controlled or not.
\end{definition}
\ednote{This definition is vague - given the vagueness of the term "quantum circuit".
 Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.}

@@

\begin{figure} % {{{
\centering
\includegraphics{OPR-circuit.pdf}
\caption{\textbf{General form of a 1PR circuit}.
Any 1PR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter.}
\label{Fig4}
\end{figure} % }}}

@@

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any 1PR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the
target qubit for the rotation, since if it is not, we could use
swap gates to move the rotation
to the first qubit without adding gates
that depend on $p$.

@@

\begin{theorem}
\label{theorem2}
Consider a 1PR circuit of $N$ qubits parametrized by $p$
and denote by $U$ the operator it implements on this system. 
Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
we have that:
\begin{align*}
U|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
\end{align*}
with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states \ednote{normal} and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
c^j|c^j \rangle = 1$.
\end{theorem}
\textbf{Proof:}  \ednote{again, this is not a conclusion from theorem 1. This is literally Definition 1. Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N. Then the matrix representation of the operators is a $2^n \times 2^n$ matrix which is applied to the state j.... The explanation in words in not sufficient.}
We can conclude from theorem 1 that $U=ARB$,
where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
applied to the last qubit and controlled by some of the other ones.

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
with $B_{i,j}$ the entries of matrix $B$.
This can be rewritten by separating the last qubit from the other $N-1$:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{align}
B|j\rangle = 
   \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle 
                                     + B_{2k+1,j} |k \rangle |1\rangle  \right) 
   + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  
                                      + B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align}

Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $R_{\sigma_3}(s(p))$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle,
\end{align}
where we defined
\begin{align*}
|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|1\rangle,\\
|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
\end{align*}
These states are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational basis. 
Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary. \ednote{true only if the initial j states are normalised, but they were undefined.}

@@

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{Fig4}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. The operators $A$ and $B$ can be defined as follows: \ednote{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?}
\begin{align*}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\end{align*}
\ednote{Please, at least give an example of this semiarbitrary construction of A and B.}
The remaining part of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary. \ednote{I don't understand what operatively is happening here. Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?}
By starting from the initial state $|0\rangle$ and 
applying the circuit shown in \fref{Fig4}, straightforward calculations 
lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.
